Process Genotypes For Ancestry Analysis

### 2019-09-20 code/Ancestry_PCA.Rmd
Chunk2V1

#Pull 1000G Data, convert to plink, Filt for INDV and SNPs
for i in {1..22}
#for i in {20..22}
do
	wget ftp://ftp-trace.ncbi.nih.gov/1000genomes/ftp/phase1/analysis_results/integrated_call_sets/ALL.chr$i\.integrated_phase1_v3.20101123.snps_indels_svs.genotypes.vcf.gz

@@

#Merge All Plink Chr Files 
for i in {2..22}
#for i in {21..22}
do
  echo 1000Genomes_chr$i >> Merge.list
done

#_#plink --bfile 1000Genomes_chr1 --merge-list Merge.list --make-bed --out 1000Genomes_Merged
plink --bfile 1000Genomes_chr20 --merge-list Merge.list --make-bed --out 1000Genomes_Merged

#rm 1000Genomes_chr*
rm *.list
rm *.panel
rm LDREF.tar.bz2
rm MergedChrs.txt

@@

## Process MSBB WGS Data
* Pull VCFs from Synapse
* Convert to plink
* Merge across chromosomes
* Filter for 1000G SNPs
```{bash ProcessMSBB, echo=FALSE}
CORES=$(nproc)
##Pull VCF Files from Synapse
mkdir VCF
synapse get -r syn11707204 --downloadLocation VCF/

for i in {22..1}
do
  vcftools --gzvcf VCF/NIA_JG_1898_samples_GRM_WGS_b37_JointAnalysis01_2017-12-08_$i.recalibrated_variants.MSSM.vcf.gz --plink --out GWAS_Plink/MSSB_Chr_$i

  rm VCF/NIA_JG_1898_samples_GRM_WGS_b37_JointAnalysis01_2017-12-08_$i.recalibrated_variants.MSSM.vcf.gz

  plink --file GWAS_Plink/MSSB_Chr_$i --threads $CORES --make-bed --allow-no-sex --snps-only --out GWAS_Plink/MSSB_Chr_$i

  rm GWAS_Plink/*$i.ped
  rm GWAS_Plink/*$i.map
done

rm GWAS_Plink/*.tbi

>>>>

#Pull 1000G Data, convert to plink, Filt for INDV and SNPs
for i in {1..22}
do
	wget ftp://ftp-trace.ncbi.nih.gov/1000genomes/ftp/phase1/analysis_results/integrated_call_sets/ALL.chr$i\.integrated_phase1_v3.20101123.snps_indels_svs.genotypes.vcf.gz

@@

#Merge All Plink Chr Files 
for i in {2..22}
do
  echo 1000Genomes_chr$i >> Merge.list
done

plink --bfile 1000Genomes_chr1 --merge-list Merge.list --make-bed --out 1000Genomes_Merged

rm 1000Genomes_chr*
rm *.list
rm *.panel
rm LDREF.tar.bz2
rm MergedChrs.txt
```

## Process MSBB WGS Data
* Pull VCFs from Synapse
* Convert to plink
* Merge across chromosomes
* Filter for 1000G SNPs
```{bash ProcessMSBB, echo=FALSE}
CORES=`expr $(nproc) - 2`
PATH=$PATH:/home/jgockley/TWAS/bin/
##Pull VCF Files from Synapse
mkdir VCF
synapse get -r syn11707204 --downloadLocation VCF/

rm VCF/NIA_JG_1898_samples_GRM_WGS_b37_JointAnalysis01_2017-12-08_X*
rm VCF/NIA_JG_1898_samples_GRM_WGS_b37_JointAnalysis01_2017-12-08_Y*
rm VCF/NIA_JG_1898_samples_GRM_WGS_b37_JointAnalysis01_2017-12-08_others*
rm -r VCF/WGS_JointCalling/
rm VCF/SYNAPSE_METADATA_MANIFEST.tsv

#Convert to PLINK
for i in {22..1}
do
  plink --vcf VCF/NIA_JG_1898_samples_GRM_WGS_b37_JointAnalysis01_2017-12-08_$i\.recalibrated_variants.MSSM.vcf.gz --threads $CORES --make-bed --allow-no-sex --snps-only --out GWAS_Plink/MSSB_Chr_$i
  rm VCF/NIA_JG_1898_samples_GRM_WGS_b37_JointAnalysis01_2017-12-08_$i\.recalibrated_variants.MSSM.vcf.*
done
rm -r VCF/

#Replace the "." IDs with a uniq ID
for i in {22..1}
do
  awk '{ print $1"\t"$1"_"$4"\t"$3"\t"$4"\t"$5"\t"$6 }' GWAS_Plink/MSSB_Chr_$i\.bim > foo.txt
  mv foo.txt GWAS_Plink/MSSB_Chr_$i\.bim
done

#Make an LD_Ref SNPList with matching name Schema
awk '{print $1"\t"$2"\t"$3"\t"$1"_"$2 }' LDREF_SNPs.txt > MSBB_LD_SNPS.txt

##Merge Chromsomes in Plink Format 
for i in {2..22} 
do 
    echo GWAS_Plink/MSSB_Chr_$i >> MergedGWAS.txt
done

CORES=`expr $(nproc) - 2`
PATH=$PATH:/home/jgockley/TWAS/bin/
plink --threads $CORES --bfile GWAS_Plink/MSSB_Chr_1 --merge-list MergedGWAS.txt --extract MSBB_LD_SNPS.txt --make-bed --allow-no-sex --out GWASTotal
#rm -r WGS_Plink/

## Process MAYO Genotyping Data
```{bash MAYO}
CORES=`expr $(nproc) - 2`
#Download
mkdir Mayo
synapse get -r syn8650955 --downloadLocation Mayo/

plink --bfile Mayo/MayoRNAseq_RNAseq_Genome-Wide_Genotypes_HRCimputed --threads $CORES --extract LDREF_SNPs.txt --range --make-bed --out Mayo_LDREF_Filt

rm -r Mayo/
#SNPS REMAINING COMPARED TO TOTAL LDREF SET:
##1,187,249 out of 1,190,321 (  99.74% )

#Rename Snps with rsIDs & Centimorgan Distance
python BimAnotator.py TotalLDRef.bim Mayo_LDREF_Filt.bim
mv Mayo_LDREF_FiltRenamed.bim Mayo_LDREF_Filt.bim

@@
